Sampling deaths and OLS

### 2018-01-21 ols.Rmd
aft

```{r}
ols$enter <- ols$enter - 60
ols$exit <- ols$exit - 60
zero <- ols$enter >= ols$exit
ols$enter[zero] <- ols$exit[zero] - 0.001 # Fix zero-length intervals (no big deal)
```

@@

```{r aft, echo = FALSE}
fit.g <- aftreg(Surv(exit, event) ~ sex, data = ols, dist = "gompertz", param = "lifeExp")
summary(fit.g)
```

>>>>

```{r}
ols$enter <- ols$enter - 60
ols$exit <- ols$exit - 60
zero <- ols$enter >= ols$exit
ols$enter[zero] <- ols$exit[zero] - 0.001 # Fix zero-length intervals (no big deal)
##ols$event[ols$exit > 30] <- 1
```

@@

```{r aft, echo = FALSE}
fit.g <- aftreg(Surv(exit, event) ~ sex + region, data = ols, dist = "gompertz", param = "lifeExp")
summary(fit.g)
em <- fit.g$baselineMean
ef <- fit.g$baselineMean * exp(fit.g$coef[1])
```
So the *e60* for Skellefteå men is `r round(em, 2)` years, and for the women we get 
`r round(ef, 2)` years, a diff of `r round(ef - em, 2)` years, that is, *men* are better off.

Compare with the result of the OLS regression:
